Windowed least-squares model reduction for dynamical systems

### 2019-10-12 main.tex
app c

where $\integrand: \RR{M}  \times \RR{M}  \times[0,T] \rightarrow  \RRplus$ (for arbitrary $M$) with $\integrand: (\stateyDiscrete,\stateyDotDiscrete,\timeDummy) \mapsto \integrand(\stateyDiscrete,\stateyDotDiscrete,\timeDummy)$. We now introduce the function $\statez: [0,T] \rightarrow \RR{M}$ that is implicitly defined as an extremum of~\eqref{eq:el_gen} subject to the boundary condition $\statez(0) = \statez_0$. 

>>>>

where $\integrand: \RR{M}  \times \RR{M}  \times[0,T] \rightarrow  \RRplus$
	(for arbitrary $M$) with $\integrand:
	(\stateyDiscrete,\stateyDotDiscrete,\timeDummy) \mapsto
	\integrand(\stateyDiscrete,\stateyDotDiscrete,\timeDummy)$. We now introduce
	the function $\statez: [0,T] \rightarrow \RR{M}$ that is implicitly defined
	as an extremum of~\eqref{eq:el_gen} subject to the boundary condition
	$\statez(0) = \statez_0$. \KTC{This previous sentence isn't correct. The
	functional defined here has two arguments; the extremum can't be a single
	argument, as it's a pair of arguments. You need to connect these by saying
	they associate with the same time-dependent funciton.} 
